The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-03 analysis/paper/paper.qmd

## TO DO: generalise bigrams and trigrams into ngrams function

## Bigrams
emu_theses_bigrams <- emu_theses |> 
  unnest_tokens(bigram, text, token = "ngrams", n = 2) |> 
  separate(bigram, into = c("first", "second"), sep = " ", remove = FALSE) |> 
  anti_join(stop_words, by = c("first" = "word")) |> 
  anti_join(stop_words, by = c("second" = "word")) |> 
  filter(str_detect(first, "[a-z]") & 
         str_detect(second, "[a-z]"))

bigram_counts <- emu_theses_bigrams |> 
  count(first, second, sort = TRUE)

bigram_counts

## Trigrams
emu_theses_trigrams <- emu_theses |> 
  unnest_tokens(trigram, text, token = "ngrams", n = 3) |> 
  separate(trigram, into = c("first", "second", "third"), sep = " ", remove = FALSE) |> 
  filter(!first %in% stop_words$word,
         !second %in% stop_words$word,
         !third %in% stop_words$word) |>  
  filter(str_detect(first, "[a-z]"), 
         str_detect(second, "[a-z]"),
         str_detect(third, "[a-z]"))

trigram_counts <- emu_theses_trigrams |> 
  count(first, second, sort = TRUE)

>>>>

## Bigrams
emu_theses_bigrams <- emu_theses |> 
  get_ngrams(n = 2, title_col = "title", text_col = "text_clean", stem = TRUE)

spacyr::spacy_parse(emu_theses_bigrams$w_1)

bigram_counts <- emu_theses_bigrams |> 
  count(w_1, w_2, sort = TRUE)

bigram_stem_counts <- emu_theses_bigrams |> 
  count(w_1_stem, w_2_stem, sort = TRUE)

bigram_counts
bigram_stem_counts

## Trigrams
emu_theses_trigrams <- emu_theses |> 
  get_ngrams(n = 3, title_col = "title", text_col = "text")

trigram_counts <- emu_theses_trigrams |> 
  count(w_1, w_2, w_3, sort = TRUE)
